Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
move back header of sec --Program synthesis for the example--
improve introduction

\item We design and implement an automatic approach for generating
  {\em corect-by-construction} digital controllers that is based on
  state-of-the-art inductive synthesis techniques.  Our application of
  program synthesis is non-trivial and requires addressing challenges
  specific to embedded control systems, such as the effects of quantizers and
  FWL. In particular, we have found that a two-stage verification engine
  that continuously refines the precision of the fixed-point
  representation is key to the performance of our approach yielding,
  in most cases, a speed-up of at least two orders of magnitude over a
  conventional one-stage verification engine.

\item We provide experimental results showing that our tool is able to
synthesize stable controllers for a set of intricate benchmarks taken from
the literature efficiently: the median runtime for our benchmark set is
$197$s, i.e., half of the controllers can be synthesized in less than five
minutes.

>>>>

\item We design and implement an automatic approach in a tool called \tool  
  for generating {\em corect-by-construction} digital controllers that is based on
  state-of-the-art inductive synthesis techniques.  Our application of
  program synthesis is non-trivial and requires addressing challenges
  specific to embedded control systems, such as the effects of quantizers and
  FWL. In particular, we have found that a two-stage verification engine
  that continuously refines the precision of the fixed-point
  representation is key to the performance of our approach yielding,
  in most cases, a speed-up of at least two orders of magnitude over a
  conventional one-stage verification engine.

\item We provide experimental results showing that \tool
is able to synthesize stable controllers for a set of intricate benchmarks 
taken from the literature efficiently: the median runtime for our benchmark 
set is $197$s, i.e., half of the controllers can be synthesized in less than 
five minutes.
